---
title: "day7 delete"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(palmerpenguins)
```

## Data wrangling refresher

1.  Starting from penguins, write a single piped sequence in which you:

    -   Only include penguins at Dream and Biscoe Islands

    -   Remove the year and sex variables

    -   Add a new column body_mass_kg with penguin mass converted from g to kg

    -   Rename the island variable to location

    ```{r}
    penguins |> 
      filter(island %in% c("Dream", "Biscoe")) |> 
      select(-year, -sex) |> 
      mutate(body_mass_kg = body_mass_g / 1000) |> 
      rename(location = island)
    ```

2.  Starting from penguins, write a single piped sequence to:

    -   Limit to Adelie penguins

    -   Remove any observations where flipper_length_mm is NA (!is.na()) or drop_na)

    -   Group the data by sex

    -   Create a summary table that contains the mean, standard deviation and sample size of flipper lengths for male and female Adelie penguins.

```{r}
adelie_summary <- penguins |> 
  filter(species == "Adelie") |> 
  drop_na(flipper_length_mm) |> 
  group_by(sex) |> 
  summarize(mean_flipper_length = mean(flipper_length_mm),
            sd_flipper_length = sd(flipper_length_mm),
            sample_size = n())
  
```

```{r}
penguins |> 
  group_by(species, island, sex) |> 
  summarize(sample_size = n())

# Count is just wrapping together group_by + summarize + n() to get counts of observations.
penguins |> count(species, island, sex)
```

```{r}
animals <- data.frame(
  stringsAsFactors = FALSE,
          location = c("lagoon", "bluff", "creek", "oaks", "bluff"),
           species = c("bobcat", "coyote", "fox", "squirrel", "bobcat"),
          maturity = c("adult", "juvenile", "adult", "juvenile", "adult")
)
```

```{r}
sites <- data.frame(
  stringsAsFactors = FALSE,
          location = c("beach", "lagoon", "bluff", "oaks"),
    full_site_name = c("Goleta Beach","UCSB Lagoon",
                       "Ellwood Mesa","Fremont Campground"),
      jurisdiction = c("SB City", "UCSB", "SB City", "USFS")
)
```

Full join:

Uses full_join()

```{r}
full_join_example <- full_join(animals, sites)
```

```{r}
left_join_example <- left_join(animals, sites)
```

```{r}
inner_join_example <- inner_join(animals, sites)-
```
